A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-07-12 draft/paper2.tex
Data and sample: edit 2

   Although these radius are empirically selected, they help recover the 
   \mstar{}-dependence of the fraction of accreted stars, and reveal the diversity of 
   stellar envelopes among massive galaxies. 
   In Figure \ref{fig:m100_m10_color}, we demonstrate such diversity by showing 
   a random subsample of massive galaxies with very similar \minn{} that have large 
   range of \mtot{}. 
   We will use these two

%% ------------------------------------------------------------------------------------ %%    
\subsection{Massive Central Galaxies from Different Environment}
    \label{ssec:cen}

    %    The \rbcg{} sample is less affected by completeness because we can utilize 
    %photo-$z$s from \redm{}. 
    %However, the completeness of the \nbcg{} sample is still limited by the 
    %availability of spec-$z$s from BOSS.\alexie{Not sure this is important here.}

    \jenny{Here is an attempt to include all the things we really need here.}

    We focus on early-type galaxies with  and stellar mass $M_*>10^{11.5}$~\msun. 
    The redshift range includes a large enough volume to have good statistics at the high-mass end, while 
    the stellar mass limit is set by our photometric incompleteness. HSC-identified objects are cross-matched 
    with the spectroscopic and photometric samples from redMapper \citep{Rykoff2014}. Stellar masses are estimated 
    using stellar population synthesis modeling of the broad-band photometry, and then the mass limit is 
    imposed. Using comparisons with published mass functions, we demonstrate that we are complete 
    to $M_*>10^{11.5}$~\msun\ over the full redshift range.

    Finally, here we wish to focus on galaxies that live at the centers of their dark matter halos. 
    We utilize the group information 
    in redMapper v5.10 \citep{Rykoff2014,Rozo2015b} to identify central galaxies. We use the 
    relation between richness $\lambda$ and stellar mass to select groups with 
    $\lambda>30$ or $M_{\rm halo}>10^{14.2}$~\msun\ \citep[e.g.,][]{simetetal2016}. This limit is chosen 
    to mitigate incompleteness at the high end of our redshift window. We then identify the 
    central galaxy to have $P_{\rm CEN}>0.7$. We will refer to this sample of 164 central galaxies as \rbcg{}. The median 
    richness of the sample is $\lambda \approx 41$ ($M_* \approx 2.2 \times 10^{14}$~\msun), and there are 
    only 44 central galaxies in clusters with $\lambda>0.5$ ($M_* > 10^{15}$~\msun). We build a complementary 
    sample of central galaxies in lower-mass halos by calculating the radius of each group with 
    $\lambda>20$ \citep{Diemer2015} and 
    then excluding galaxies within a cylinder around each group, with the thickness of the cylinder broadened to include 
    photo-z uncertainty. The sample of {\bf XX} central galaxies living in halos with $M_* < 10^{14}$~\msun\ will 
    be called \nbcg{}.

@@

    %\footnote{There are different observational definitions of ``environment''. 
    %In this paper, we use the term ``environment'' and halo mass interchangeably}.

    \song{These paragraphs are from Jenny's txt file, need organization.}
    Massive central galaxies in this work show an intriguing diversity on the plane 
    defined by these two metrics.  
    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z{\sim} 0.4$ that share very similar value of \minn{}, but 
    exhibit a large diversity in their outer profiles. 
    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
    it is of great interest to investigate the relation between their present day halo 
    mass and the extend of their outer envelopes. 
    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
    for our mass measurements, we always use elliptical apertures that follow the 
    average isophotal shape. Finally, given our narrow mass and redshift range, we 
    can safely ignore significant mass growth and structural evolution in this work
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).

    \textbf{Completeness that depends on halo mass:}

@@

%%%%%%%%%%: Appendix Section %%%%%%%%%%%%

@@

\song{Just copied a couple of relevant sections here; need some works}
%% ------------------------------------------------------------------------------------ %% 
\section{A. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
    \label{app:gama}

@@

\section{B. Comparisons of \mden{} profiles in different redshift bins}
    \label{app:redshift}

@@

\section{C. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
    \label{app:match}

@@

%% ------------------------------------------------------------------------------------ %% 
\section{D. Robustness of the \mden{} Differences} 
	\label{app:robust}

>>>>

   Although these radius are empirically selected, they help recover the 
   \mstar{}-dependence of the fraction of accreted stars, and reveal the diversity of 
   stellar envelopes among massive galaxies. 
   In Figure \ref{fig:m100_m10_color}, we demonstrate such diversity by showing 
   a random subsample of massive galaxies with very similar \minn{} that have large 
   range of \mtot{}. 
   We will use these two apertures\mstar{} to guide the comparisons of massive galaxies 
   from different environments.

%% ------------------------------------------------------------------------------------ %%    
\subsection{Massive Central Galaxies from Different Environments}
    \label{ssec:cen}

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that the \mstar{} completeness above this threshold is 
    good over the full redshift range using comparisons with stellar mass functions 
    from more complete samples.

    We also wish to focus on massive galaxies that live at the centers of their own 
    dark matter halos-- so-called ``central'' galaxies.  
    They are uniquely important to the study of galaxy-halo connection and are known 
    to follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
    Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{} end with small scatter.
    We utilize the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
    to identify central galaxies.

    Firstly, we select 68 massive central galaxies from the \redm{} clusters 
    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/69 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness of low richness clusters
    at the high end of our redshift window, and the $P_{\mathrm{Cen}}$ limit is 
    selected to exclude low probability candidate of central galaxy. 
    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
    galaxies are the brightest cluster galaxies (BCGs) of clusters with 
    \mhalo{}$>10^{14.2}$~\msun{}.
    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in more massive halos} as 
    the \rbcg{} sample.

    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
    \citet{Simet2016}. 
    Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
    \citet{Diemer2015}. 
    And we exclude all galaxies within a cylinder around each cluster, with the radius
    equal to $R_{\mathrm{200b}}$ and length equal to twice the value of the photometric 
    redshift uncertainty (typically around 0.015 to 0.025). 
    We generally consider this sample as the central galaxies living in halos with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}.
    Initially, we select 3453 galaxies this way with \logmtot{}$> 11.2$ at 
    $0.3 < z < 0.5$. 
    Among them, 1564 (833) have \logmtot{}$> 11.5$ (11.6). 
    Satellite contamination should be relative low at the high-\mtot{} end
    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
    For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
    contamination in the \logmtot{}$>11.6$ sample from satellites from 
    \logmh$<11.4$ haloes.

    It is worth noting that we failed to extract 1-D profiles for $\sim10$\% of 
    \rbcg{} and \nbcg{} galaxies due to physical (e.g. on-going major merger) or 
    nuisance (e.g.\ nearby foreground galaxy or bright star) reasons. 
    These situations happen more frequently for lower-\mtot{} galaxies, and should not 
    affect the results of this work.

@@

    Massive central galaxies in this work show an intriguing diversity on the plane 
    defined by these two metrics.  
    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z{\sim} 0.4$ that share very similar value of \minn{}, but 
    exhibit a large diversity in their outer profiles. 
    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
    it is of great interest to investigate the relation between their present day halo 
    mass and the extend of their outer envelopes. 
    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
    for our mass measurements, we always use elliptical apertures that follow the 
    average isophotal shape. Finally, given our narrow mass and redshift range, we 
    can safely ignore significant mass growth and structural evolution in this work
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).

@@

%% ------------------------------------------------------------------------------------ %% 
%% Appendix Section
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\section{A. Basic Statistical Properties of the Sample} 
	\label{app:sedasic}

    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
    relations using the $k$-corrected $g-r$ color. 
    Both samples follow the same tight ``red-sequence'' with little contamination 
    from the ``blue cloud''.
    At fixed \mtot{}, we see little offset in color distributions of the two 
    samples, suggesting that both samples consist of quiescent galaxies with 
    similar average stellar population properties.  
    This is consistent with previous result that suggests the average stellar 
    population of massive central galaxy does not depend on \mhalo{} 
    (e.g.\ \citealt{Park2007}).  
    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
    where both samples have acceptable completeness, and their \mtot{} distributions 
    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
    panel of Fig~\ref{fig:sample_stats}). 
    As for the \minn{} distributions, the two samples overlap the most within 
    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
    distributions (bottom-right figure).

    The redshift distributions also show small difference
    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
    spec-$z$.
    Since this could bias the comparison of \mden{} profiles and other properties 
    (please see Appendix\ref{app:redshift} for more details), we address this via matching 
    the two samples in both mass and redshift distributions carefully
    (see Appendix~\ref{app:match}).

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
      }
      \label{fig:sample_stats}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{B. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
    \label{app:gama}

@@

\section{C. Comparisons of \mden{} profiles in different redshift bins}
    \label{app:redshift}

@@

\section{D. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
    \label{app:match}

@@

%% ------------------------------------------------------------------------------------ %% 
\section{E. Robustness of the \mden{} Differences} 
	\label{app:robust}
